---
title: "pipeline"
author: "Zihan Li"
date: "2024-11-29"
output: html_document
---

## Introduction

This pipeline:
-   (1) reads in all individual subject voxel data with stimuli and coordinates data;
-   (2) streams the individualized data to iterated lasso module and output selected voxels activation data of each subject combined with activation and coordinate data;
-   (3) trains final glmnet models with L2 norm and extracts model coefficients to combine with coordinates information;
-   (4) clusters voxels of each subject to specify categories of voxels;
-   (5) creates visualized results of clustered voxels for similarity/difference comparison.

## Dependencies

```{r message=F}
# Packages
library(tidyverse)
library(glmnet)
library(ggplot2)

# Self-defined functions
ilasso_path <- "./zihan_ilasso_functions/"
ilasso_functions <- list.files(path = ilasso_path,
                               pattern = "\\.R$",
                               full.names = T)
invisible(sapply(ilasso_functions, source))
```

Individual directories have been created by `individual_data_div.R`. See the file for more details.

## Divide original data

```{r}
data_path <- "./fpo_data_all"
stim <-  "fpo_tr5_allParticipants_stimuli.csv"
coord <- "fpo_tr5_allParticipants_coordinates.csv"
individual_data_div(data_path = data_path, stim_file = stim, coord_file = coord)
```

## Read in data

```{r}
# Read in data for all subjects in a list
data <- individual_data_read()
```

# Iterated Lasso, L2 Fitting and Clustering

```{r}
# Change `use_cache` to F when arguments are modified.
clustered_data <- individual_data_process(data, nfold = 10, max_iter = 10, seed=137, use_cache = T)
```

## Save individually clustered data

```{r}
out_dir <- "./output"
if (!dir.exists(out_dir)) {
    dir.create(out_dir)
}

for (name in names(clustered_data)){
  out_data <- clustered_data[[name]]$result$data_clustered
  out_filename <- file.path(out_dir, paste0(name, ".csv"))
  write_csv(out_data, file = out_filename)
  cat("Saved:", out_filename, "\n")
}

```










